Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
Image add

\subsection{Link encoding as subgraphs union}
\label{sec:link}
Most methods for link prediction compute pairwise nodes similarities treating  the nodes defining the candidate edge independently. Instead we propose to jointly consider both candidate endpoint nodes together with their extended ''context''. To do so we build a graph starting from the two nodes and the underlying network. Given nodes $u$ and $v$, we first extract the two neighborhood sets with a user defined radius $R$ rooted at $u$ and $v$ to obtain $N_R(u)$ and $N_R(v)$, respectively. We then consider the graph $\mathcal{J}$ induced by the set union $N_R(u) \cup N_R(u)$. Finally we add an auxiliary node $w$ and the necessary edges to connect it to $u$ and $v$ (see Fig.\ref{key}).
\figurename{fig:g}

@@

In the link prediction problem we are given a graph $G(V,E)$ and a binary target vector $Y=\{y_{(0,0)},y_{(0,1)}, \cdots, y_{(|V|,|V|)}\}$ where $y_{(u,v)}=1$ if $(u,v) \in E$ and 0 otherwise. The training data is obtained considering a random subset of edges in $E^{tr} \in E$ and inducing a training graph $G^{tr}=(V,E^{tr})$. The remaining edges $E^{ts} = E \setminus E^{tr}$ are used to partition the target vectors: $Y^{tr} = \{y_{(u,v)} | (u,v) \in E^{tr}\}$, $Y^{ts} = \{y_{(u,v)} | (u,v) \in E^{ts}\}$.
We can now cast the problem as a standard classification problem in the domain of graphs. Given $G^{tr}$ we build a train and test set as the corresponding joint neighborhood subgraphs as detailed in Section~\ref{sec:link}. 
We can now compute a Gram matrix of the instances and solve the classification task using for example the efficient LinearSVC library.

@@

>>>>

\subsection{Link encoding as subgraphs union}
\label{sec:link}
Most methods for link prediction compute pairwise nodes similarities treating  the nodes defining the candidate edge independently. Instead we propose to jointly consider both candidate endpoint nodes together with their extended ''context''. To do so we build a graph starting from the two nodes and the underlying network. Given nodes $u$ and $v$, we first extract the two neighborhood sets with a user defined radius $R$ rooted at $u$ and $v$ to obtain $N_R(u)$ and $N_R(v)$, respectively. We then consider the graph $\mathcal{J}$ induced by the set union $N_R(u) \cup N_R(u)$. Finally we add an auxiliary node $w$ and the necessary edges to connect it to $u$ and $v$ (see Fig.\ref{fig:example}).
\begin{figure}
\centering
\includegraphics[height=2.2cm]{subgraphs}
\caption{Example of joint neighborhood subgraphs.}
\label{fig:example}
\end{figure}

@@

In the link prediction problem we are given a graph $G(V,E)$ and a binary target vector $Y=\{y_{(0,0)},y_{(0,1)}, \cdots, y_{(|V|,|V|)}\}$ where $y_{(u,v)}=1$ if $(u,v) \in E$ and 0 otherwise. The training data is obtained considering a random subset of edges in $E^{tr} \in E$ and inducing a training graph $G^{tr}=(V,E^{tr})$. The remaining edges $E^{ts} = E \setminus E^{tr}$ are used to partition the target vectors: $Y^{tr} = \{y_{(u,v)} | (u,v) \in E^{tr}\}$, $Y^{ts} = \{y_{(u,v)} | (u,v) \in E^{ts}\}$.
We can now cast the problem as a standard classification problem in the domain of graphs. Given $G^{tr}$ we build a train and test set as the corresponding joint neighborhood subgraphs as detailed in Section~\ref{sec:link}. 
We can now compute a Gram matrix of the instances and solve the classification task using for example the efficient LinearSVC library \cite{svm}.

@@

\bibitem{svm} http://www.scikit-learn.org/
